---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Convert manifest.json to renv.lock

As the R community moves away from packrat towards its successor, renv, it is becoming increasingly more commonplace to convert from packrat to renv. But how can we take a manifest.json file and turn it into an renv.lock.

The file `manifest-to-renv.R` creates a function to do this using a not-yet-exported R6 object from {renv}. This functionality is subject to change.

Below is the function definition. 

```{r}
library(renv)
library(tidyverse)

# Create empty lockfile. Use system call because it will be completely empty
# system("touch renv.lock")

manifest_to_renv <- function(manifest) {
  if (!file.exists("renv.lock")) {
    rlang::inform("Creating an empty renv.lock file.")
    file.create("renv.lock")
  }
  
  # create R6 objec
  lock <- renv:::lockfile(file = "renv.lock")  

  # read in manifest
  manifest <- jsonlite::read_json(manifest)
  
  # extract dependencies
  depends <- manifest$packages %>% 
    map_chr(pluck, "description", "Version") %>% 
    enframe() %>% 
    mutate(purl = glue::glue("{name}@{value}"))
  
  # extract repos
  repos <- manifest$packages %>% 
    map_chr(pluck, "Source") %>% 
    enframe() %>% 
    mutate(repo = map_chr(manifest$packages, pluck, "Repository")) %>% 
    distinct(value, repo) %>% 
    deframe() %>% 
    as.list()
  
  # update repos
  do.call(lock$repos, repos)
  
  # convert deps
  deps_list <- depends %>% 
    select(name, purl) %>% 
    deframe() %>% 
    as.list()
  
  # update dependencies
  do.call(lock$add, deps_list)
  
  # write the lockfile
  lock$write("renv.lock")
  # what is missing is the R version.
}
```

Below creates an `renv.lock` file from the `manifest.json` file.

```{}
manifest_to_renv("manifest.json")
```

